Improving credibility and efficiency of decision-making \\ within democratic communities via statistical quorum

### 2018-04-19 statistical-quorum.tex
Updating methodology.

For the baseline, we extracted similar information from council minutes: how long did the councils last, how many
discussions were opened, how many comments by which members were made, how many proposals were proposed,
and vote tallies for them.

@@

We evaluate statistical quorum in two ways. First, we analyze it theoretically and explore its mathematical properties.
Then we evaluate it through real-world use of the PeerMind application by a 140 members community.

>>>>

For the baseline, we extracted similar information from council minutes: how long did the councils last,
how many members participated, how many proposals were proposed and how many passed, and vote tallies for them.

@@

We evaluate statistical quorum in two ways. First, we analyze it theoretically and explore its mathematical properties.
Then we do qualitative and quantitative evaluation through real-world use of the PeerMind application by a 140 members
community.
